### 2009-01-19 doc/sec/SecurityFrameworkofARC1.tex
Enhancing description of delegation interface, adding diagrams.

\date{2008-12-23}

@@

\begin{flushleft}
\bottomcaption{Security Attributes collected at SOAP MCC}
\tablehead{\hline
\centering \selectlanguage{english}\bfseries\itshape\color{black}
Element &
\centering \selectlanguage{english}\bfseries\itshape\color{black}
AttributeId &
\centering\arraybslash
\selectlanguage{english}\bfseries\itshape\color{black}
Content\\\hline}\begin{supertabular}{|m{1.2330599in}|m{2.5476599in}|m{1.7698599in}|}
\selectlanguage{english}\color{black} Resource &
\selectlanguage{english}\color{black}
http://www.nordugrid.org/schemas/policy-arc/types/soap/endpoint &
\selectlanguage{english}\color{black} To element of WS-Addressing
structure\\\hline
\selectlanguage{english}\color{black} Action &
\selectlanguage{english}\color{black}
http://www.nordugrid.org/schemas/policy-arc/types/soap/operation &
\selectlanguage{english}\color{black} SOAP top level element name
without namespace prefix\\\hline
\selectlanguage{english}\color{black} Context &
\selectlanguage{english}\color{black}
http://www.nordugrid.org/schemas/policy-arc/types/soap/namespace &
\selectlanguage{english}\color{black} Namespace of SOAP top level
element\\\hline
\end{supertabular}
\end{flushleft}
\subsection[Delegation Restrictions]{Delegation Restrictions}
\label{bkm:Ref204009393}\subsubsection[Delegation
Architecture]{Delegation Architecture}
\label{bkm:Ref204009914}{\selectlanguage{english}\upshape\color{black}
In current implementation delegation is achieved through Identity
Delegation implemented using X509 Proxy Certificates as defined in RFC
3820. Client wishing to allow service to act on it{\textquotesingle}s
behalf provides Proxy Certificate to the service using Web Service
based Delegation interface described in Section \ref{bkm:Ref204009766}}

@@

\subsubsection[Delegation interface]{Delegation interface}
\label{bkm:Ref204009766}{\selectlanguage{english}\upshape\color{black}
Delegation interface in the ARC1 is implemented using Web Service
approach. Each ARC1 service wishing to accept delegated credentials
implements this interface. Here is how delegation procedure works:}

\liststyleWWviiiNumix
\begin{itemize}
\item {\selectlanguage{english}\color{black}
Step 1}
\item {\selectlanguage{english}\color{black}
Client contacts service requesting operation DelegateCredentialsInit.
This operation has no arguments.}
\item {\selectlanguage{english}\color{black}
Service responds with DelegateCredentialsInitResponse message with
element TokenRequest. That element contains credentials request
generated by service in Value. Type of request is defined by attribute
Format. Currently only supported format is x509. Along with Value
service provides identifier Id which is used in second step.}
\end{itemize}
\liststyleWWviiiNumx
\begin{itemize}
\item {\selectlanguage{english}\color{black}
Step 2}
\item {\selectlanguage{english}\color{black}
Client requests UpdateCredentials operation with DelegatedToken
argument. This element contains Value with serialized delegated
credentials and Id which links it to first step. Delegated token
element may also contain multiple Reference elements. Reference refers
to the object which these credentials should be applied to in a way
specific to the service. The DelegatedToken element may also be used
for delegating credentials when Step 2 is combined with other
operations on service in service specific way.}
\item {\selectlanguage{english}\color{black}
Service responds with empty UpdateCredentialsResponse message.}
\end{itemize}
\subsection[Schemas, descriptions and examples]{Schemas, descriptions
and examples}
\subsubsection[Authorization Policy]{Authorization Policy}
\label{bkm:Ref204009564}{\selectlanguage{english}\upshape\color{black}
XML schema with comments available at
\url{http://svn.nordugrid.org/trac/nordugrid/browser/arc1/trunk/src/hed/pdc/arcpdp/Policy.xsd}
.}

@@

\begin{center}
\includegraphics[width=3.2256in,height=1.8472in]{SecurityFrameworkofARC1-img7.png}
\end{center}

@@

{\centering\selectlanguage{english}\itshape\color{black}
Figure \stepcounter{Figure}{\theFigure}.\textbf{ }SAML2.0 SSO profile in
ARC
\par}

{\selectlanguage{english}\color{black}
\ The steps shows in Figure 6 are described as follows:}

@@

{\selectlanguage{english}\color{black}
\ \ \ \ The SLCS service is also a Web Service (standard Web Service
implemented by using ARC service interface), and the SLCS client is a
specific command-line interface (CLI) which includes the user agent and
WS client. The whole process of SLCS invocation is showed in Figure 7
(from step 1 to step 8), which is the same as in Figure 6, except that
step 7 and step 8 are invoked for the SLCS certificate request and
response.}

\begin{center}
\includegraphics[width=3.7689in,height=3.2055in]{SecurityFrameworkofARC1-img8.png}
\end{center}
{\centering\selectlanguage{english}\itshape\color{black}
Figure \stepcounter{Figure}{\theFigure}.Short lived credential service
\par}

>>>>

\date{2009-01-19}

@@

\begin{flushleft}
\bottomcaption{Security Attributes collected at SOAP MCC}
\tablehead{\hline
\centering \selectlanguage{english}\bfseries\itshape\color{black}
Element &
\centering \selectlanguage{english}\bfseries\itshape\color{black}
AttributeId &
\centering\arraybslash
\selectlanguage{english}\bfseries\itshape\color{black}
Content\\\hline}\begin{supertabular}{|m{1.2330599in}|m{2.5476599in}|m{1.7698599in}|}
\selectlanguage{english}\color{black} Resource &
\selectlanguage{english}\color{black}
http://www.nordugrid.org/schemas/policy-arc/types/soap/endpoint &
\selectlanguage{english}\color{black} To element of WS-Addressing
structure\\\hline
\selectlanguage{english}\color{black} Action &
\selectlanguage{english}\color{black}
http://www.nordugrid.org/schemas/policy-arc/types/soap/operation &
\selectlanguage{english}\color{black} SOAP top level element name
without namespace prefix\\\hline
\selectlanguage{english}\color{black} Context &
\selectlanguage{english}\color{black}
http://www.nordugrid.org/schemas/policy-arc/types/soap/namespace &
\selectlanguage{english}\color{black} Namespace of SOAP top level
element\\\hline
\end{supertabular}
\end{flushleft}
\subsection[Delegation]{Delegation}
\label{bkm:Ref204009393}\subsubsection[Delegation
Architecture]{Delegation Architecture}
\label{bkm:Ref204009914}{\selectlanguage{english}\upshape\color{black}
In current implementation delegation is achieved through Identity
Delegation implemented using X509 Proxy Certificates as defined in RFC
3820. Client wishing to allow service to act on it{\textquotesingle}s
behalf provides Proxy Certificate to the service using Web Service
based Delegation interface described in Section \ref{bkm:Ref204009766}}

@@

\subsubsection[Delegation interface]{Delegation interface}
\label{bkm:Ref204009766}{\selectlanguage{english}\upshape\color{black}
Delegation interface in the ARC1 is implemented using Web Service
approach. Each ARC1 service wishing to act on behalf of client identity
implements this interface in order to accept delegated credentials.
Here is how delegation procedure works (also shown in figures
\ref{seq:refFigure7} and \ref{seq:refFigure8}) :}

\liststyleWWviiiNumix
\begin{itemize}
\item {\selectlanguage{english}\color{black}
Step 1}
\item {\selectlanguage{english}\color{black}
Client contacts service requesting operation DelegateCredentialsInit.
This operation has no arguments.}
\item {\selectlanguage{english}\color{black}
Service responds with DelegateCredentialsInitResponse message with
element TokenRequest. That element contains credentials request
generated by service in Value. Type of request is defined by attribute
Format. Currently only supported format is x509. Along with Value
service provides identifier Id which is used in second step.}
\end{itemize}
\liststyleWWviiiNumx
\begin{itemize}
\item {\selectlanguage{english}\color{black}
Step 2}
\item {\selectlanguage{english}\color{black}
Client requests UpdateCredentials operation with DelegatedToken
argument. This element contains Value with serialized delegated
credentials and Id which links it to first step. Delegated token
element may also contain multiple Reference elements. Reference refers
to the object which these credentials should be applied to in a way
specific to the service. The DelegatedToken element may also be used
for delegating credentials when Step 2 is combined with other
operations on service in service specific way.}
\item {\selectlanguage{english}\color{black}
Service responds with empty UpdateCredentialsResponse message.}
\end{itemize}
{\selectlanguage{english}\color{black}
Optionally step 2 can be skipped and the DelegatedToken element provided
to Service as additional payload of other service specific message. }

{\selectlanguage{english}\color{black}
The Id element obtained in the step 1 can be reused multiple times with
different content of the Value element.}

{\selectlanguage{english}\color{black}
WSDL of portType implementing delegation functionality can be found at
\url{http://svn.nordugrid.org/trac/nordugrid/browser/arc1/trunk/src/hed/libs/delegation/delegation.wsdl}
.}

{\centering [Warning: Draw object ignored]\par}

{\centering\selectlanguage{english}\itshape\color{black}
Figure {\refstepcounter{Figure}\theFigure\label{seq:refFigure7}}. The
flow diaram of delegation procedure with multiple second step and
session expiration. 
\par}

{\centering [Warning: Draw object ignored]\par}

{\centering\selectlanguage{english}\itshape\color{black}
Figure {\refstepcounter{Figure}\theFigure\label{seq:refFigure8}}. The
flow diagram of delegation procedure with certificate transfered as
payload of service specific message. 
\par}

\subsection[Schemas, descriptions and examples]{Schemas, descriptions
and examples}
\subsubsection[Authorization Policy]{Authorization Policy}
\label{bkm:Ref204009564}{\selectlanguage{english}\upshape\color{black}
XML schema with comments available at
\url{http://svn.nordugrid.org/trac/nordugrid/browser/arc1/trunk/src/hed/pdc/arcpdp/Policy.xsd}
.}

@@

@@

{\centering 
\includegraphics[width=3.2256in,height=1.8472in]{SecurityFrameworkofARC1-img7.png}
\par}

{\centering\selectlanguage{english}\itshape\color{black}
Figure
{\refstepcounter{Figure}\theFigure\label{seq:refFigure5}}.\textbf{
}SAML2.0 SSO profile in ARC
\par}

{\selectlanguage{english}\color{black}
\ The steps shows in Figure \ref{seq:refFigure5} are described as
follows:}

@@

{\selectlanguage{english}\color{black}
\ \ \ \ The SLCS service is also a Web Service (standard Web Service
implemented by using ARC service interface), and the SLCS client is a
specific command-line interface (CLI) which includes the user agent and
WS client. The whole process of SLCS invocation is showed in Figure
\ref{seq:refFigure6} (from step 1 to step 8), which is the same as in
Figure \ref{seq:refFigure5}, except that step 7 and step 8 are invoked
for the SLCS certificate request and response.}

\begin{center}
\includegraphics[width=3.7689in,height=3.2055in]{SecurityFrameworkofARC1-img8.png}
\end{center}
{\centering\selectlanguage{english}\itshape\color{black}
Figure {\refstepcounter{Figure}\theFigure\label{seq:refFigure6}}.Short
lived credential service
\par}
